% ----- DOCUMENT CLASS ----- %
\documentclass[letterpaper]{article}

% ----- PACKAGES ----- %
\usepackage[empty]{fullpage}        % remove default margins/header space
\usepackage{titlesec}               % section title formatting
\usepackage{enumitem}               % list spacing control
\usepackage[hidelinks]{hyperref}    % clickable links, no boxes
\usepackage{fancyhdr}               % blank header/footer
\usepackage[english]{babel}         % hyphenation patterns
\usepackage[dvipsnames]{xcolor}     % NavyBlue and other named colors
\input{glyphtounicode}              % map glyphs to Unicode (ATS-readable text)

% ----- FONTS ----- %
\usepackage[sfdefault]{noto-sans}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ----- SET FOOTSKIP ----- %
\setlength{\footskip}{3.60004pt}

% ----- MARGINS ----- %
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{NavyBlue}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensures generated PDF is machine / ATS readable %
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% ===== RESUME STARTS HERE ===== %

\begin{document}

% ----- RESUME HEADER ----- %
\begin{center}
    {\color{NavyBlue}\textbf{\huge \scshape Stanley Cheung}} \\
    \vspace{5pt}
    \href{https://github.com/cheuyin}{\underline{github.com/cheuyin}} $|$
    \href{mailto:yinstanleycheung@gmail.com}{\underline{yinstanleycheung@gmail.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of British Columbia}{September 2022 -- May 2027}
      {B.Sc, Major in Computer Science}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{\textbf{Courses}: Machine Learning, Computer Networking, Relational Databases, Algorithms \& Data Structures, Computer Systems \& Hardware, Object-Oriented
Programming}
        \resumeItem{\textbf{Awards:} 2025 Dean's List, 2024 Charles \& Jane Banks Scholarship, 2023 Dean's List}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer Intern $|$ \normalfont{TypeScript, Express.js, PostgreSQL, AWS, React}}{January 2024 -- July 2024}
      {VoltSafe Inc.} {Vancouver, BC}
        \resumeItemListStart
          \resumeItem{Designed and implemented an end-to-end role-based access control system with an Express.js, PostgreSQL, and AWS Cognito backend, ensuring controlled access to the
  internal admin dashboard.}
          \resumeItem{Developed and Dockerized a server monitoring system using React, Express, and Prometheus, enabling real-time collection and analysis of CPU, RAM, and disk metrics
across 7+ EC2 web and database servers.}
          \resumeItem{Developed an image and document storage system with a RESTful API for the marina management app, using AWS S3 to optimize performance and reduce bandwidth
costs and allowing users to upload, store, and retrieve documents and images.}
          \resumeItem{Conducted a performance analysis of the marina management app using Chrome Lighthouse, reducing total app bundle size by 22\% by pruning unused static assets,
leading to improved load times.}
        \resumeItemListEnd

      \resumeSubheading
        {AP Computer Science Instructor}{October 2022 -- February 2023}
        {iSmart Education Canada}{Vancouver, BC}
        \resumeItemListStart
          \resumeItem{Designed and taught weekly CS lessons on algorithms, data structures, and Java programming.}
          \resumeItem{Exceeded expectations by supporting students, some still in primary school, in achieving 5/5 on the AP CSA 2023 exam.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{UBC Course Explorer} $|$ TypeScript, React, Express.js, Node.js $|$ \href{https://github.com/cheuyin/ubc-course-explorer}{\underline{github.com/cheuyin/ubc-course-explorer}}}
          \resumeItemListStart
            \resumeItem{Built a full-stack analytics app for exploring 64,000+ UBC course sections across 189 departments, featuring grade-trend charts, instructor and department profiles, and a campus room finder, using React 19, TanStack Query, and an Express + TypeScript REST API.}
            \resumeItem{Implemented a JSON query language supporting nested boolean filters (AND/OR/NOT), wildcard string matching, multi-key sorting, and GROUP-BY aggregations (MAX/MIN/AVG/SUM/COUNT), with a validation layer that returns precise field-level error messages; verified by 100+ integration tests.}
            \resumeItem{Engineered an asynchronous data-ingestion pipeline that unzips raw archives, parses course JSON, and scrapes building/room data from HTML (parse5) into a file-backed store, with job-status polling endpoints for long-running uploads and no external database.}
          \resumeItemListEnd


      \resumeProjectHeading
        {\textbf{Local AI Coding Agent} $|$ Python, Google Gemini API, Rich $|$ \href{https://github.com/cheuyin/ai-agent-python}{\underline{github.com/cheuyin/ai-agent-python}}}
          \resumeItemListStart
            \resumeItem{Engineered an autonomous agentic loop using the Google Gemini API, dispatching file system tool calls across up to 20 iterative model rounds until task
completion.}
            \resumeItem{Implemented context window management that tracks prompt token usage per round and trims conversation history when approaching the 1M-token limit, enabling
indefinitely long sessions.}
            \resumeItem{Blocked path traversal attacks via \texttt{os.path.commonpath} validation on all file operations; implemented 3-attempt exponential backoff retry for transient
API failures.}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Pathfinding Visualizer} $|$ TypeScript, React, HTML5 Canvas $|$ \href{https://pathfindingvisualizer.com}{\underline{https://cheuyin.github.io/pathfinding-visualizer/}}}
          \resumeItemListStart
            \resumeItem{Built a web app for visualizing pathfinding algorithms (Dijkstra's, A*, and DFS) and random maze-generation algorithms.}
            \resumeItem{Rewrote the rendering pipeline from React DOM to HTML5 Canvas with \texttt{requestAnimationFrame} loops and applied \texttt{React.memo}/\texttt{useCallback} memoization, cutting redundant renders 86\% (115,000 to 16,000) and raising frame rate 8--10x (7 to 60+ FPS).}
            \resumeItem{Set up a Continuous Deployment pipeline using GitHub Actions to automate deployment when pushed to main branch.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages:}{ TypeScript, Python, SQL, R, Java, C, JavaScript} \\
        \textbf{Frameworks:}{ FastAPI, React, Express.js, SQLModel, LangChain } \\
        \textbf{Other:}{ Node.js, PostgreSQL, Docker, Git, AWS, RESTful APIs, SQL ORMs, Linux, Prompt Engineering} \\
        \textbf{Certifications:}{ AWS Certified Cloud Practitioner}
    }}
  \end{itemize}

%-------------------------------------------
\end{document}